### 2017-03-12 CO750-ApproximationAlgorithmsTopics/assignments/assignment_02.tex
starting to write p3

x&\in \Z,

@@

x\in \Z

@@

\end{document}

>>>>

x&\in \Z^{|E|},

@@

x\in \Z^{|E|}

@@

%Q3
\section{}
\paragraph{}
Consider again the problem $(IP)$, associated with a graph $G=(V,E)$ with edges costs $c: E \rightarrow \R_+$ given by:
\begin{align*}
\min\ \sum_{e\in E} c(e) x_e&\\
\text{s.t.}\  \sum_{e\in\delta(S)} x_e &\geq f(S) &\forall S \subseteq V \\
x&\geq 0 \\
x&\in \Z^{|E|}.
\end{align*}
Suppose that $f:2^V \rightarrow \N$ is symmetric, meaning for all $S\subseteq V$:
$$f(S) = f(V\backslash S)$$
and that $f$ is subadditive, meaning for all $A,B \subseteq V$:
$$f(A\cup B) \leq f(A) + f(B).$$
We also suppose that the graph $G$ is a cycle on $n$ vertices.
%3a
\subsection*{a}
\paragraph{}
We begin by working towards a compact formulation for $(IP)$ on $G$. Since $G$ is a cycle we may label the vertices of $G$ as $V(G) = \{v_1,\dots, v_n\}$ such that $v_iv_j \in E(G)$ if and only if $$j \equiv i\pm1\mod n$$. For $i, \ell \in [n]$ ($[n] := \{1,\dots, n\}$) we define the path from $i$ of length $\ell$ as 
$$P(i, \ell) := \{v_i, v_{i+1}, \dots, v_{i + \ell} \}$$
where addition is taken modulo $n$. We use the convention that when $\ell = n$ we have the entire cycle, and when $\ell = 0$ we have just $v_i$. We define the family of paths on $G$ to as
$$\cP := \{P(i,\ell) : i, \ell \in [n]\}.$$
Observe that the size of $\cP$ is polynomial in $n$, in particular $|\cP| = O(n^2)$.
\begin{lemma}\label{lemma:compact}
The problem $(IP)$ on $G$ is equivalent to the compact integer program $(\overline{IP})$ given by:
\begin{align*}
\min\ \sum_{e\in E} c(e) x_e&\\
\text{s.t.}\  \sum_{e\in\delta(P)} x_e &\geq f(P) &\forall P \in \cP \\
x&\geq 0 \\
x&\in \Z^{|E|}.
\end{align*}
\end{lemma}
\begin{proof}

\end{proof}
%3b
\subsection*{b}
\end{document}
